### 2017-03-31 manuscript/publication-conclusion.tex
Takeout thinkstep footnote

Before the goal of easily reproducible foreground models can be realized, the linked data foundation must be laid.   The four entity classes found in foreground studies, namely foreground flows, background processes, elementary flows, and characterization quantities, must shift from being recorded locally to being stored on the Semantic Web, where their shared meaning can be curated.  Fortunately, this is easy to do: authoritative sources simply need to publish hyperlinks to their content. Providers of aggregated inventory data should make available static hyperlinks to their content, so that licensees and data users can make shared reference to the same entities, even if the data may not be accessible to the general public. Thinkstep already does this: every process inventory they publish has a stable link on the Web\footnote{\href{http://gabi-documentation-2016.gabi-software.com/xml-data/processes/f8dddbcb-f08c-4217-99de-0b59d2c11bb1.xml}{http://gabi-documentation-2016.gabi-software.com/xml-data/processes/[UUID].xml} where [UUID] is replaced with the process's unique identifier. For example, \texttt{f8dddbcb-f08c-4217-99de-0b59d2c11bb1} corresponds to production of 1,3-Butadiene, via catalytic dehydrogenation of butane, in Germany in 2015.}.  Similarly, impact assessment providers should publish their characterization data in a way that allows for automatic query and validation.  Both of these tasks can be accomplished independently through the efforts of members of the LCA community; however, the accuracy and validity of the data would be improved if the work were done by the data providers themselves.

>>>>

Before the goal of easily reproducible foreground models can be realized, the linked data foundation must be laid.   The four entity classes found in foreground studies, namely foreground flows, background processes, elementary flows, and characterization quantities, must shift from being recorded locally to being stored on the Semantic Web, where their shared meaning can be curated.  Fortunately, this is easy to do: authoritative sources simply need to publish hyperlinks to their content. Providers of aggregated inventory data should make available static hyperlinks to their content, so that licensees and data users can make shared reference to the same entities, even if the data may not be accessible to the general public. %Thinkstep already does this: every process inventory they publish has a stable link on the Web\footnote{\href{http://gabi-documentation-2016.gabi-software.com/xml-data/processes/f8dddbcb-f08c-4217-99de-0b59d2c11bb1.xml}{http://gabi-documentation-2016.gabi-software.com/xml-data/processes/[UUID].xml} where [UUID] is replaced with the process's unique identifier. For example, \texttt{f8dddbcb-f08c-4217-99de-0b59d2c11bb1} corresponds to production of 1,3-Butadiene, via catalytic dehydrogenation of butane, in Germany in 2015.}.
Similarly, impact assessment providers should publish their characterization data in a way that allows for automatic query and validation.  Both of these tasks can be accomplished independently through the efforts of members of the LCA community; however, the accuracy and validity of the data would be improved if the work were done by the data providers themselves.
